Development of a 3D display

### 2017-01-14 paper.tex
use \frac{...}{...} instead of \si{ ... \per ...}
fixed typo, used siunitx more

\item Resolution of $16 \cdot 100 \cdot 10$ pixels (radius $\cdot$ circumference $\cdot$ height)
\item Each pixel consists of an RGB LED
\item Colour depth of 3 bit per pixel, or one bit per LED
\item Rotational frequency of at least 30 Hz, or as fast as it needs to be in order to not flicker

@@

For controlling the LEDs, I have bought a Teensy 3.1 microcontroller development board
\cite{teensy}. It has a small footprint --- ideal for the fast rotation --- and still packs quite
some power. The processor runs at 96 MHz at a register width of 32 bit, and there are 34
configurable I/O pins.

@@

If the colour depth is more than one bit, the LEDs will have to be dimmed using PWM. Normally, a
rather low frequency of a few hundred to a few thousand Hz is sufficient as a PWM frequency, and
most LED drivers modulate at frequencies within that range. In my case, however, the LEDs are
moving into a new pixel 3000 times a second (assuming rotationat 30 Hz). This means that a PWM
frequency under 3000 Hz will involve losing information, and one slightly above 3000 Hz still
won't look good. There would have to be a significant number of PWM cycles within each pixel,
for example 10, which would require a PWM frequency of 30 KHz.

@@

In order to achieve this, but also to avoid large gaps between the pixels, I placed the LEDs as
close as possible to each other. The datasheet claims a width of \SI{2.8 \pm 0.2}{\milli\meter},
so I decided to place the LEDs at \SI{3}{\milli\metre} increments. On a grid of \SI{12.5}{mil},
the next larger distance is \SI{125}{mil}, which is equal to \SI{3.175}{mm}.

@@

\begin{ownmath}
\textrm{P\textsubscript{MAX}} = (\SI{5}{\volt} - \textrm{V\textsubscript{F}}) \cdot
\SI{20.6}{\milli\ampere\per output} \cdot \SI{16}{outputs} = \SI{780}{\milli\watt}
\end{ownmath}

@@

It turned out that the culprit were the bad contacts. Instead of soldering the wires onto the
board and the microcontroller, I simply inserted them into the respective holes. This caused the
connection to have too much parasitic capacitance, and the signals (which were being sent at 4
MHz) did not have time to propagate up to their destination.

>>>>

\item Resolution of $16 \cdot 100 \cdot 10$ pixels (radius $\cdot$ circumference $\cdot$ height)
\item Each pixel consists of an RGB LED
\item Colour depth of 3 bit per pixel, or one bit per LED
\item Rotational frequency of at least \SI{30}{\hertz}, or as fast as it needs to be in order
	to not flicker

@@

For controlling the LEDs, I have bought a Teensy 3.1 microcontroller development board
\cite{teensy}. It has a small footprint --- ideal for the fast rotation --- and still packs quite
some power. The processor runs at \SI{96}{\mega\hertz} at a register width of 32 bit, and there
are 34 configurable I/O pins.

@@

If the colour depth is more than one bit, the LEDs will have to be dimmed using PWM. Normally, a
rather low frequency of a few hundred to a few thousand Hz is sufficient as a PWM frequency, and
most LED drivers modulate at frequencies within that range. In my case, however, the LEDs are
moving into a new pixel 3000 times a second (assuming rotation at 30 Hz). This means that a PWM
frequency under 3000 Hz will involve losing information, and one slightly above 3000 Hz still
won't look good. There would have to be a significant number of PWM cycles within each pixel,
for example 10, which would require a PWM frequency of \SI{30}{\kilo\hertz}.

@@

In order to achieve this, but also to avoid large gaps between the pixels, I placed the LEDs as
close as possible to each other. The datasheet claims a width of \SI{2.8 \pm 0.2}{\milli\meter},
so I decided to place the LEDs at \SI{3}{\milli\metre} increments. On a grid of \SI{12.5}{mil},
the next larger distance is \SI{125}{mil}, which is equal to \SI{3.175}{\milli\metre}.

@@

\begin{ownmath}
\textrm{P\textsubscript{MAX}} = (\SI{5}{\volt} - \textrm{V\textsubscript{F}}) \cdot
\num{20.6} \frac{\si{\milli\ampere}}{{\text{output}}} \cdot \SI{16}{outputs} = \SI{780}{\milli\watt}
\end{ownmath}

@@

It turned out that the culprit were the bad contacts. Instead of soldering the wires onto the
board and the microcontroller, I simply inserted them into the respective holes. This caused the
connection to have too much parasitic capacitance, and the signals (which were being sent at
\SI{4}{\mega\hertz}) did not have time to propagate up to their destination.
